An Extensible Approach to Verification of Embedded Network Systems*

### 2014-04-22 tech-project/paper.tex
updated paper

\subsection{C Translation Model}
One of the primary challenges in translating from RESOLVE to C is finding a suitable C analog for each RESOLVE module and the constructs allowable in each. Indeed, since we are dealing with an environment where functional correctness is a primary concern, it is important that the code generated by our tool represents as closely as possible the original RESOLVE source. In an effort to make such considerations, at the highest level, the C code generated makes special considerations for facilities, concepts, and realizations.

The relationship between the RESOLVE module type and c code generated is depicted at a high level in Figure \#.

Unsurprisingly, concepts are represented in C by a single header .h listing the various methods

>>>>

\subsection{C Translation Model}
One of the primary challenges in translating from RESOLVE to C is finding a suitable C analog for each RESOLVE module and the constructs allowable in each. Indeed, since we are dealing with an environment where functional correctness is a primary concern, it is important that the code generated by our tool represents as closely as possible the original RESOLVE source. In an effort to make such considerations, at the highest level, the C code generated makes special considerations for facilities, concepts, and realizations. Another such consideration includes memory, and decisions on dynamic or static allocation. RESOLVE does not currently provide specifications towards a memory model but is in aspirations of providing a dynamically allocatable system. Following suit, we will introduce a stack based memory allocator in section \#.

The relationship between the RESOLVE module type and c code generated is depicted at a high level in Figure \#. Unsurprisingly, concepts are represented in C by a single header \texttt{.h}. Some realizations connected to concepts are \texttt{externally} realized, denoting that they are not generated from RESOLVE. Additionally concepts can be \texttt{enhanced by} adding new enhancement components to the concept. RESOLVE facilities then produce corresponding \texttt{.h/c} files that provides the application interface implementation of concepts.

%Unsurprisingly, concepts are represented in C by a single header .h listing the various methods
